Climate-RWI relations

### 2018-01-04 analysis/rwi/climate_rwi_relate.Rmd
update tree-climate

```{r packages, warning=FALSE, message=FALSE, echo=FALSE}
library("tidyverse")
library("stringr")
library("treeclim")
# devtools::install_github("thomasp85/patchwork")
library("patchwork")
```

@@

```{r}
eobs <- read.csv(file=paste0(di, "data/eobs/eobs_formatted.csv"), header=TRUE, sep=',')

# sanjuan: 37.133, -3.382 = spei_-3.25_37.25.csv 
# canar: 36.957, -3.4284 = spei_-3.25_36.75.csv

@@

@@

@@

```{r rwi_cli_prec_spei}
p_prec_spei <- p_prec + p_spei + plot_layout(ncol=1)
pdf(paste0(di, '/out/climate_rwi/prec_spei.pdf'), width=9, height = 8)
p_prec_spei
dev.off()
```

>>>>

```{r packages, warning=FALSE, message=FALSE, echo=FALSE}
library("tidyverse")
library("stringr")
library("treeclim")
# devtools::install_github("thomasp85/patchwork")
library("patchwork")
library("readr")
```

@@

# Spei data: 0.5 º - 1950

```{r}
# sanjuan: 37.133, -3.382 = spei_-3.25_37.25.csv 
# canar: 36.957, -3.4284 = spei_-3.25_36.75.csv

@@

# Spei data: 1.1 km º - 1961 (4 for months )
```{r}
# http://monitordesequia.csic.es/ 
# sanjuan: 37.13, -3.37 = DATA_37.13_-3.37.csv
# canar Low: 36.956, -3.424 = DATA_36.96_-3.42.csv
# canar High: 36.966, -3.421 = DATA_36.97_-3.42.csv

spei_sjD <- read.csv(file=paste0(di, "data_raw/spei/monitor_sequia/DATA_37.13_-3.37.csv"), header=TRUE)
spei_caHD <- read.csv(file=paste0(di,  "data_raw/spei/monitor_sequia/DATA_36.97_-3.42.csv"), header=TRUE)  
spei_caLD <- read.csv(file=paste0(di,  "data_raw/spei/monitor_sequia/DATA_36.96_-3.42.csv"), header=TRUE)

# Prepare data 
sequia_sj <- spei_sjD %>% 
  mutate(date = parse_date(DATA, format='%d-%B-%Y', locale = locale('es')),
         year = lubridate::year(date),
         month = lubridate::month(date)) %>% 
  dplyr::select(year, month, spei6 = spei_6) %>% 
  filter(year > 1961) %>% 
  group_by(year, month) %>% 
  summarise(spei6 = mean(spei6)) %>% as.data.frame()

sequia_caH <- spei_caHD %>% 
  mutate(date = parse_date(DATA, format='%d-%B-%Y', locale = locale('es')),
         year = lubridate::year(date),
         month = lubridate::month(date)) %>% 
  dplyr::select(year, month, spei6 = spei_6) %>% 
  filter(year > 1961) %>% 
  group_by(year, month) %>% 
  summarise(spei6 = mean(spei6)) %>% as.data.frame()

sequia_caL <- spei_caLD %>% 
  mutate(date = parse_date(DATA, format='%d-%B-%Y', locale = locale('es')),
         year = lubridate::year(date),
         month = lubridate::month(date)) %>% 
  dplyr::select(year, month, spei6 = spei_6) %>% 
  filter(year > 1961) %>% 
  group_by(year, month) %>% 
  summarise(spei6 = mean(spei6)) %>% as.data.frame()

@@

# SPEI High-resol

```{r}
set.seed(3333)
rsequia_SJ <- dcc(chrono = cro_sj, climate = sequia_sj, 
         method = "correlation",  boot = "std", var_names = 'spei6',
        .range(-3:9) + .mean(-9:8) + .mean(-12:2) + .mean(3:5) + .mean(6:8) + .mean(9:11))

rsequia_caL <- dcc(chrono = cro_caL, climate = sequia_caL, 
         method = "correlation",  boot = "std", var_names = 'spei6',
        .range(-3:9) + .mean(-9:8) + .mean(-12:2) + .mean(3:5) + .mean(6:8) + .mean(9:11))

rsequia_caH <- dcc(chrono = cro_caH, climate = sequia_caH, 
         method = "correlation",  boot = "std", var_names = 'spei6',
        .range(-3:9) + .mean(-9:8) + .mean(-12:2) + .mean(3:5) + .mean(6:8) + .mean(9:11))

# Joins dccs 
rsequias <- c('rsequia_SJ', 'rsequia_caH', 'rsequia_caL')
rsequia_all <- join_dccs(rsequias)

rsequia_all <- customNames(rsequia_all) 
```

## Plot SPEI HR
```{r rwi_clim_sequia}
p_sequia <- rsequia_all %>% ggplot(aes(x=id, y=coef, group = site)) + 
  custom_gg +
  scale_x_continuous(breaks = rsequia_all$id, labels = rsequia_all$month_name) + 
  theme(legend.position = c(.1, .8)) +
  annotate("text", label = "SPEI 6 - HR", x = 1, y= -0.4) 
p_sequia

pdf(paste0(di, '/out/climate_rwi/sequia.pdf'), width=9, height = 5)
p_sequia
dev.off()
```

@@

```{r rwi_cli_prec_spei_sequia}
p_prec_spei <- p_prec + p_spei + p_sequia + plot_layout(ncol=1)
pdf(paste0(di, '/out/climate_rwi/prec_spei.pdf'), width=9, height = 8)
p_prec_spei
dev.off()
```

```{r rwi_cli_prec_sequia}
p_prec_sequia <- p_prec + p_sequia + plot_layout(ncol=1)
pdf(paste0(di, '/out/climate_rwi/prec_sequia.pdf'), width=9, height = 8)
p_prec_sequia
dev.off()
```
